% Bibliografia

\addcontentsline{toc}{chapter}{Bibliografie}
\markboth{\sc Bibliografie}{\sc Bibliografie}

%\small{

\begin{thebibliography}{99}

\bibitem{tf} Abadi, Martín, Paul Barham, Jianmin Chen, Zhifeng Chen, Andy Davis, Jeffrey Dean, Matthieu Devin et al. "Tensorflow: A system for large-scale machine learning." In 12th {USENIX} symposium on operating systems design and implementation ({OSDI} 16), pp. 265-283, 2016.

\bibitem{bellman-theory} Bellman, Richard, On the Theory of Dynamic Programming, National Academy of Sciences, 1952

\bibitem{anomaly} Chalapathy, R. and Chawla, S., Deep learning for anomaly detection: A survey, 2019

\bibitem{nn-book-2} Chris M. Bishop , "Neural networks and their applications", Review of Scientific Instruments 65, 1803-1832 (1994)

\bibitem{nn-book-3} Dumitrescu D., Haritoni Costin, Re@tele Neuronale, Teora, 1996

\bibitem{smooth-function-aprox}	Ferrari, Silvia \& Stengel, Robert, Smooth Function Approximation Using Neural Networks. Neural Networks, 2005

\bibitem{gpt} Floridi, L. and Chiriatti, M., 2020. GPT-3: Its nature, scope, limits, and consequences. Minds and Machines, 30(4), pp.681-694.

\bibitem{open-ai-gym-env-format} Greg Brockman and Vicki Cheung and Ludwig Pettersson and Jonas Schneider and John Schulman and Jie Tang and Wojciech Zaremba, OpenAI Gym, CoRR, 2016

\bibitem{facebook-ml} Hazelwood, Kim, Sarah Bird, David Brooks, Soumith Chintala, Utku Diril, Dmytro Dzhulgakov, Mohamed Fawzy et al. "Applied machine learning at facebook: A datacenter infrastructure perspective." In 2018 IEEE International Symposium on High Performance Computer Architecture (HPCA), pp. 620-629. IEEE, 2018.

\bibitem{donald-hebb-book} Hebb, D. O.  The organization of behavior : a neuropsychological theory / D.O. Hebb, Wiley New York, 1949

\bibitem{q-learning-book-2} Hester, T., Vecerik, M., Pietquin, O., Lanctot, M., Schaul, T., Piot, B., Horgan, D., Quan, J., Sendonaris, A., Osband, I. and Dulac-Arnold, G.,  April. Deep q-learning from demonstrations. In Proceedings of the AAAI Conference on Artificial Intelligence, 2018

\bibitem{hornik-nn} Hornik, Kurt, Approximation capabilities of multilayer feedforward networks, Neural Networks, 1991

\bibitem{react-book} Jonathan Hayward, Artemij Fedosejev, Narayan Prusty, Adam Horton, Ryan Vice, Ethan Holmes, Tom Bray, React: Building Modern Web Applications, Packt Publishing, 2016    

\bibitem{nvidia-gan} Karras, Tero, Timo Aila, Samuli Laine, and Jaakko Lehtinen. "Progressive growing of gans for improved quality, stability, and variation.", 2017

\bibitem{nn-book-4} R@adac Mircea-Bogdan, Tehnici de @inv@a@tare automat@a cu aplica@tii, Editura Politehnica, 2019

\bibitem{svelte-book} Scherer, Justin, Hands-on JavaScript high performance : build faster web apps using Node.js, Svelte.js, and WebAssembly, Packt Publishing, 2020

\bibitem{reinforcement-learning} Sutton, Richard S., and Andrew G. Barto. Reinforcement learning: An introduction. MIT press, 2018.

\bibitem{double-q} Van Hasselt, Hado, Arthur Guez, and David Silver. "Deep reinforcement learning with double q-learning." In Proceedings of the AAAI Conference on Artificial Intelligence, vol. 30, no. 1, 2016.

\bibitem{q-learning-book-1} Watkins, C.J. and Dayan, P., Q-learning. Machine learning, 8(3-4), pp.279-292., 1992

\bibitem{deepfakes} Westerlund, M., 2019. The emergence of deepfake technology: A review. Technology Innovation Management Review, 9(11).

\bibitem{nn-book-1} Yegnanarayana, B., Artificial Neural Networks, Prentice-Hall of India Pvt.Ltd. 2004

\bibitem{smooth-curve-aproximation} Zhou, Zhenghua and Zhao, Jianwei, Approximation of Curves Contained on the Surface by Freed-Forward Neural Networks, Springer Berlin Heidelberg, 2011

\bibitem{netscape} "Netscape and Sun announce JavaScript", PR Newswire, 4 decembrie, 1995

\bibitem{arthur-samuel} \begin{verbatim}
	http://infolab.stanford.edu/pub/voy/museum/samuel.html
\end{verbatim}

\bibitem{ibm-unsupervised-learning} \begin{verbatim}
	https://www.ibm.com/cloud/learn/unsupervised-learning
\end{verbatim}

\bibitem{eu-big-data-definition} \begin{verbatim}
	https://www.europarl.europa.eu/news/ro/headlines/society/20210211STO97614/
\end{verbatim}

\bibitem{Svelte} \begin{verbatim} https://svelte.dev
\end{verbatim}

\bibitem{React} \begin{verbatim} https://reactjs.org
\end{verbatim}

\bibitem{Vue} \begin{verbatim} https://vuejs.org
\end{verbatim}

\bibitem{Angular} \begin{verbatim} https://angular.io
\end{verbatim}

\bibitem{diagrame-exemplu} \begin{verbatim} https://echarts.apache.org/examples/en/index.html
\end{verbatim}

\bibitem{Echarts} \begin{verbatim} http://echarts.apache.org/en/index.html
\end{verbatim}

\bibitem{TensorflowJs} \begin{verbatim} https://www.tensorflow.org/js
\end{verbatim}

\bibitem{Konva} \begin{verbatim} https://konvajs.org/docs/index.html
\end{verbatim}

\end{thebibliography}

